---
title: "NMCC Behavioral and Eyetracking Results"
output: html_document
params:
  data: 'Study1b'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# must adjust this to file location
dataPath <- paste('~/Dropbox/Studies/Dissertation/output/', params$data, '/', sep='') 

library(itrackR)
library(edfR)
library(dplyr)
library(dtplyr)
library(ggplot2)
library(lme4)
library(haven)
library(lmerTest)
library(effects)
library(psych)

excludeRTmax <- 2000
excludeRTmin <- 100
excludeRTmaxSDs <- 3

load(paste(dataPath, 'cleanDataBehAnalyses.Rda', sep='')) 
load(paste(dataPath, 'eyetrackingData_byTrial.Rda', sep='')) 

# Center continuous predictor variables 
cleanData_behAnalyses$Trial_Ctr <- cleanData_behAnalyses$Trial - 2.5
cleanData_behAnalyses$Block_Ctr <- (cleanData_behAnalyses$Block - 4) - 6.5


```
All analyses use linear mixed models with fixed slopes and random intercepts.

# Behavioral Analyses

## Reaction Time (RT)
RTs were transformed using the natural log to reduce skewness. Outliers greater than 3SDs from each participant's mean RT for each condition, as well as RTs > 2000ms or <100ms

```{r RT data cleaning include=FALSE }
# Data cleaning for RT analyses: 
# Remove error trials, Non-Switch blocks, first sets of blocks, and trials 5 and 6.
cleanData <- filter(cleanData_behAnalyses, Error==0, Blocktype>2, Set>1, Trial<5)

# log transform RTs and find outliers
cleanData$lnRT <- log(cleanData$RT)
findOutliers <- group_by(cleanData, ID, Trial, switchSet, Congruent, Blocktype) %>%
  summarise(meanlnRT=mean(lnRT, na.rm=TRUE),
            sdlnRT=sd(lnRT, na.rm=TRUE))
findOutliers$exclude <- findOutliers$meanlnRT + excludeRTmaxSDs*findOutliers$sdlnRT
findOutliers$excludeMin <- findOutliers$meanlnRT - excludeRTmaxSDs*findOutliers$sdlnRT
cleanData <- merge(cleanData, findOutliers, by='ID', sort=FALSE)
cleanData$outlierMax <- cleanData$exclude-cleanData$lnRT
cleanData$outlierMin <- cleanData$excludeMin-cleanData$lnRT

# create factors
cleanData$switchSet <- factor(cleanData$switchSet,
                              levels=c(0,1),
                              labels=c('Non-Switch Set','Switch Set'))

cleanData$Congruent <- factor(cleanData$Congruent,
                              levels=c(1,2),
                              labels=c('Congruent','Incongruent'))

cleanData$Blocktype <- factor(cleanData$Blocktype,
                              levels=c(3,4),
                              labels=c('Pure Updating','Perseveration-Inhibition'))
cleanData$ID <- factor(cleanData$ID)

# remove outliers
cleanData_outliersRemoved <- filter(cleanData, 
                                    RT>=excludeRTmin & RT<=excludeRTmax & outlierMax>0 & outlierMin<0)
```

### Null Model

```{r null model RT, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
